Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-18 ms.tex
note to self
added figure showing posterior PDF examples

@@

>>>>

% for CO line list see ~/wise/pro/planck_co_lines.pro

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded osterior PDFs for three nside=2048 pixels. Red crosses mark 
the best-fit parameters based on our Markov Chain sampling of the posterior. 
The posterior distributions are in general extremely well-behaved, showing
no multimodality, and our MCMC parameter estimates coincide well with the
peaks in the gridded posteriors. The colorscale is linear in log(P), with black representing the maximum of log(P) and white represent max(log(P))-5. Left: Low S/N pixel at high-latitude in 
Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N pixel at high-latitude in the Galactic 
south. }
\end{center}
\end{figure*}
